---
name: Brent Schneeman
position: "Senior Director, Data Science"
address: "1903 Barton Parkway, Austin TX 78704"
phone: 512.298.8880
www: schneeworld.netlify.com
email: "schneeman@gmail.com"
twitter: schnee
github: schnee
linkedin: schneeman
headcolor: 686868
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::moderncv
  

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Overview

I focus mainly on building a data science and algorithmic muscle, but also get to work on building durable teams . I think visually and don't feel comfortable with a data set unless I can craft an aesthetically pleasing image out of it. I am quite comfortable telling stories in front of crowds of any size and seeks avenues to expand the role of science and math in all directions. I pivoted from software engineering roles to data science to help companies unlock the value of their data as they pivoted to modern transaction-based business models.
 
# Experience

```{r experience}
my_experience <- tibble::tribble(
  ~title, ~start, ~end, ~company, ~why,
  "Senior Director, Data Science", "Jan 2018", "", "DOSH, LLC", "Built a diverse team of Data Scientists, Data Analysts, and Data Engineers, all focused on evolving Dosh to a more data-oriented company. The Data and Analytics team was responsible for Data Science, Business Intelligence and Data Engineering (e.g. the data warehouse and data lake)",
  "Senior Director, Data Science", "Jan 2018", "", "DOSH, LLC", "Collaborated with key business stakeholders to generate marketing campaigns, financial models, sales models, and investor-deck content",
  "Senior Director, Data Science", "Jan 2018", "", "DOSH, LLC", "Collaborated with technical stakeholders to create a data warehouse from application data and to create data pipelines feeding location data to S3 buckets for graph analysis. Eliminated redundant RDBMS systems in-favor of AWS Redshift",
  "Senior Director, Data Science", "Jan 2018", "", "DOSH, LLC", "Built xgboost-based models predicting offer redemption (directly tied to revenue) and deeply analyzed fraudulent behaviors and referral networks",
  "Senior Director, Data Science", "Jan 2018", "", "DOSH, LLC", "Lead transformation of company dashboards from 'vanity-metrics' to business-focused KPIs",
  "Senior Director, Data Science", "Jan 2018", "", "DOSH, LLC", "Directed Data Science efforts in predicting causal impact of multi-vendor markets and price elasticity",
  "Senior Director, Data Science", "Sep 2016", "Dec 2017", "HomeAway, an Expedia Company", "Strengthening Data Science muscle through project-based leadership. Partnering with disparate product lines to answer questions quicker, and find new questions faster. Evangelizing data-informed decision making.",
  "Senior Director, Data Science", "Sep 2016", "Dec 2017", "HomeAway, an Expedia Company", "Competitive intelligence, fraud detection, unstructured data mining.",
  "Senior Director, Data Science", "Sep 2016", "Dec 2017", "HomeAway, an Expedia Company", "Bayesian and frequentist multi-variate test analysis. Evangelizing data-informed decision making",
  "Senior Director, Data Science", "Sep 2016", "Dec 2017", "HomeAway, an Expedia Company", "Introduced natural language processing, machine learning and defensible statistical inference",
  "Senior Director, Data Science", "Sep 2016", "Dec 2017", "HomeAway, an Expedia Company", "Created and lead 100+ volunteer \"science club\", all trying to swipe right for science",
  "Principal Data Scientist", "Jun 2014", "Sept 2016", "HomeAway, an Expedia Company", "Partnered with the UT McCombs School of Business, providing guidance and data for the Business Analytics program participant capstone projects. Acted as an external ambassador through public speaking at various events."
)

my_experience %>% detailed_entries(
  what = title,
  when = glue::glue("{start} - {end}"),
  with = company, 
  why = why
)

```
