\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{hyperref}   % For clickable links
\usepackage{titlesec}   % For customizing section headings
\usepackage{enumitem}   % For better control of list spacing
\usepackage{parskip}    % For spacing between paragraphs (no indents)

\setlength{\parindent}{0pt}

% Customize section headings
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\titlerule]
\titleformat{\subsection}{\bfseries\normalsize}{}{0pt}{}

\begin{document}

\begin{center}
{\LARGE \textbf{Brent Schneeman}}\\
\textbf{AI Solutions Architect}\\[6pt]
Austin, TX \quad | \quad 512.298.8880 \quad | \quad \href{mailto:schneeman@gmail.com}{schneeman@gmail.com}\\
GitHub: \href{https://github.com/schnee}{schnee} \quad | \quad LinkedIn: \href{https://linkedin.com/in/schneeman}{schneeman}
\end{center}

\vspace{1em}
\hrule
\vspace{1em}

%=====================
% SUMMARY OF QUALIFICATIONS
%=====================
\section*{SUMMARY OF QUALIFICATIONS}
AI Solutions Architect with extensive experience designing, implementing, and leading end-to-end machine learning systems. Combines deep technical expertise with leadership and cross-functional collaboration skills to architect real-time, data-driven products that bring measurable business impact. Adept at bridging software engineering, data science, MLOps, and stakeholder management.

\textbf{Highlights}:
\begin{itemize}[leftmargin=*]
  \item Architected and deployed large-scale ML pipelines (using AWS, Snowflake, DBT, Prefect, and Kubernetes) to operationalize AI models for diverse industries.
  \item Designed active learning frameworks, NLP-driven solutions, and real-time computer vision applications.
  \item Built and led global teams of software engineers, data scientists, and ML/AI specialists, driving innovation from concept to production.
  \item Frequent advisor to executive stakeholders, translating business objectives into robust AI roadmaps and solution architectures.
\end{itemize}

%=====================
% KEY AREAS OF EXPERTISE
%=====================
\section*{KEY AREAS OF EXPERTISE}
\begin{itemize}[leftmargin=*]
  \item \textbf{Architecting AI Solutions:} End-to-end system design, real-time deployment, microservices, DevOps/MLOps
  \item \textbf{Cloud \& Infrastructure:} AWS (EC2, S3, Lambda, Sagemaker), Kubernetes, Kubeflow, Snowflake, DBT
  \item \textbf{Machine Learning \& Data Science:} NLP, CV, deep learning (PyTorch, Keras), active learning, model ops
  \item \textbf{Programming Languages:} Python, R, SQL, Java
  \item \textbf{Leadership \& Collaboration:} Agile/Scrum, cross-functional team management, stakeholder alignment, executive advising
\end{itemize}

%=====================
% SELECT ACHIEVEMENTS
%=====================
\section*{SELECT ACHIEVEMENTS}
\begin{itemize}[leftmargin=*]
  \item \textbf{LLM-Driven Candidate Screening:} Led design \& implementation of a Large Language Model (LLM) platform for automated candidate assessment, increasing candidate NPS by 12\%.
  \item \textbf{AI-Optimized Advertising Content:} Deployed a GenAI pipeline to predict key ad-performance metrics and streamline creative processes for CMO-level stakeholders.
  \item \textbf{Real-Time Scheduling Optimization:} Implemented an algorithmic scheduling solution reducing time-to-schedule by 50\% and overall service time by 20\%.
  \item \textbf{Active Learning Architecture:} Built a scalable workflow coupling human annotation with machine learning for image/video tasks, cutting annotation costs significantly.
  \item \textbf{Multinational Data Team Expansion:} Formed global Data Science \& Analytics organizations, establishing local hiring pipelines in the US \& Europe.
\end{itemize}

%=====================
% PROFESSIONAL EXPERIENCE
%=====================
\section*{PROFESSIONAL EXPERIENCE}

\subsection*{Director, Software and AI \hfill PMG (Feb 2024 -- Present, Austin, TX)}
\begin{itemize}[leftmargin=*]
  \item Oversee AI \& Software Engineering teams, architecting ML solutions to optimize ad content and KPI performance.
  \item Utilize GenAI and classical ML methods, integrating real-time APIs and iterative feedback loops to transform marketing analytics.
\end{itemize}

\subsection*{AI Consultant \hfill Thought and Memory LLC}
\textit{(Jan 2024 -- Mar 2024)}
\begin{itemize}[leftmargin=*]
  \item Collaborated with PMG to design the foundational ML architecture for ad content performance models.
  \item Guided team hiring \& technical ramp-up for first production ML capabilities.
\end{itemize}

\textit{(Jan 2023 -- Sep 2023)}
\begin{itemize}[leftmargin=*]
  \item Created an LLM-based intake and feedback system for candidate interviews, integrating with cloud-based services to automate scoring \& analysis.
\end{itemize}

\textit{(Sep 2022 -- Dec 2022)}
\begin{itemize}[leftmargin=*]
  \item Architected a jobsite maintenance scheduling system using advanced optimization libraries, accelerating scheduling cycles by 50\%.
\end{itemize}

\subsection*{Vice President, Data Science and Analytics \hfill Overhaul, Inc. (Jun 2020 -- Aug 2022)}
\begin{itemize}[leftmargin=*]
  \item First data-focused hire; envisioned \& built the architecture for data ingestion, analytics, and ML pipelines (DBT, Prefect, Snowflake).
  \item Implemented transportation duration models \& security event scoring for real-time supply chain monitoring.
  \item Deployed an international team across the US \& Ireland, partnering with local universities and recruiters to expand AI capabilities.
\end{itemize}

\subsection*{Senior Director, Machine Learning \hfill Alegion, Inc. (Mar 2019 -- Apr 2020)}
\begin{itemize}[leftmargin=*]
  \item Drove core ML architecture, including a hybrid AWS Sagemaker / Kubernetes environment for CV \& NLP workflows.
  \item Introduced version-controlled data pipelines (Kubeflow, DVC) to ensure reproducible, scalable AI deployments.
  \item Oversaw IP filings \& new product SKUs, bridging ML R\&D with client-facing solutions.
\end{itemize}

\subsection*{Senior Director, Data Science \hfill DOSH, LLC (Jan 2018 -- Feb 2019)}
\begin{itemize}[leftmargin=*]
  \item Established a 9-person Data Team to architect a modern data warehouse (AWS Redshift) \& predictive models (XGBoost) for user reward redemptions.
  \item Led cross-functional initiatives to unify siloed data, enabling real-time fraud detection and location-based analytics.
\end{itemize}

\subsection*{Senior Director \& Director, Data Science \& Software Engineering \hfill HomeAway (Expedia) (Jun 2010 -- Dec 2017)}
\begin{itemize}[leftmargin=*]
  \item \textbf{Data Science:} Built and managed a 25-person ML team delivering solutions in search ranking, NLP chatbots, and image analysis.
  \item \textbf{Software Engineering:} Led 25-person dev group responsible for PCI-compliant payments, designing robust APIs for global transactions.
  \item Created advanced ML pipelines, introduced word2vec-based recommendation engines, and championed data-driven product development.
\end{itemize}

\subsection*{Principal Software Engineer \& Manager \hfill PayPal, Inc. (Mar 2007 -- Jun 2010)}
\begin{itemize}[leftmargin=*]
  \item Delivered two-factor authentication (hardware token) for PayPal/eBay platforms.
  \item Introduced Agile methods and served as a Certified ScrumMaster to modernize team workflows.
\end{itemize}

\subsection*{Software Engineer \hfill Visa, Inc. (Nov 2000 -- Mar 2007)}
\begin{itemize}[leftmargin=*]
  \item Led development of Verified by Visa directory servers (3-D Secure), managing certification and compliance efforts.
\end{itemize}

%=====================
% EDUCATION
%=====================
\section*{EDUCATION}
\begin{itemize}[leftmargin=*]
  \item \textbf{Complex Systems Summer School}, The Santa Fe Institute (2015)
  \item \textbf{B.S. in Electrical Engineering}, University of Southern California (1990)
  \item \textbf{B.A. in Mathematics}, Carroll College (1990)
\end{itemize}

%=====================
% VOLUNTEERING & AFFILIATIONS
%=====================
\section*{VOLUNTEERING \& AFFILIATIONS}
\begin{itemize}[leftmargin=*]
  \item \textbf{Industry Adviser}, UT McCombs School of Business (2015 -- Present): Providing input on ML curricula; ran three capstone projects
  \item \textbf{Advisory Council}, McCombs School of Business, University of Texas (Jan 2014 -- Present)
  \item \textbf{Chairman of the Board / Board Member}, Skillpoint Alliance (Feb 2012 -- Sep 2016)
  \item \textbf{Industry Consultant}, City of Austin Business \& International Affairs Focus Group (Jan 2018 -- Present)
\end{itemize}

%=====================
% CERTIFICATIONS
%=====================
\section*{CERTIFICATIONS}
\begin{itemize}[leftmargin=*]
  \item Neural Networks and Deep Learning (Python/Keras), Coursera (Nov 2017)
  \item R Programming, Coursera (Sept 2014)
  \item The Data Scientist’s Toolbox, Coursera (Sept 2014)
  \item Certified ScrumMaster, Rally, Inc. (June 2008)
\end{itemize}

%=====================
% PATENTS
%=====================
\section*{PATENTS}
\begin{itemize}[leftmargin=*]
  \item \textbf{US9928498B2 (2018-03-27)} -- System, apparatus and method for segregating data in transactions via dedicated interface elements for isolated logic and repositories
  \item \textbf{US10339487B2 (2019-07-02)} -- Systems and methods to reconcile free-text with structured data
\end{itemize}

\vspace{1em}
\hrule
\vspace{0.5em}
\noindent \textit{References available upon request}

\end{document}
