\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{hyperref}   % for clickable links
\usepackage{titlesec}   % for customizing section headings
\usepackage{enumitem}   % for better control of list spacing
\usepackage{parskip}    % for spacing between paragraphs (no indents)

\setlength{\parindent}{0pt}

% Customize section headings
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\titlerule]
\titleformat{\subsection}{\bfseries\normalsize}{}{0pt}{}

\begin{document}

\begin{center}
{\LARGE \textbf{Brent Schneeman}}\\
\textbf{Head of AI | Engineering \& Data Science}\\[6pt]
Austin, TX \quad | \quad 512.298.8880 \quad | \quad \href{mailto:schneeman@gmail.com}{schneeman@gmail.com}\\
GitHub: \href{https://github.com/schnee}{schnee} \quad | \quad LinkedIn: \href{https://linkedin.com/in/schneeman}{schneeman}
\end{center}

\vspace{1em}
\hrule
\vspace{1em}

%=====================
% SUMMARY OF QUALIFICATIONS
%=====================
\section*{SUMMARY OF QUALIFICATIONS}
AI and machine learning executive with extensive experience in building and scaling cross-functional data organizations and real-time algorithmic products. Skilled at blending software engineering, leadership, and advanced analytics to drive bottom-line impact. Adept at partnering with C-level stakeholders to shape AI strategy, deploy novel ML solutions, and lead global teams toward data-centric innovation.

\textbf{Highlights}:
\begin{itemize}[leftmargin=*]
  \item Founded and led multiple data/AI teams (ranging from startups to large enterprises), delivering predictive models, real-time analytics, and advanced ML pipelines.
  \item Repeated success aligning ML strategy with broader business goals—demonstrated revenue impact via new SKUs, reduced costs, and improved operational efficiency.
  \item Hands-on technical leadership in machine learning (NLP, CV, deep learning), cloud architecture (AWS, Kubernetes), MLOps (Kubeflow, DBT, Snowflake), and big data tools (Spark, Hadoop).
\end{itemize}

%=====================
% KEY AREAS OF EXPERTISE
%=====================
\section*{KEY AREAS OF EXPERTISE}
\begin{itemize}[leftmargin=*]
  \item \textbf{Leadership \& Strategy:} Executive collaboration, organizational design, agile methodologies, product roadmapping
  \item \textbf{AI \& ML Engineering:} Deep learning (PyTorch, Keras), active learning workflows, CV, NLP
  \item \textbf{Data Architecture \& Infrastructure:} MLOps (Kubeflow, DVC), AWS (Lambda, Sagemaker, S3), Snowflake, DBT, Python, R, SQL
  \item \textbf{Project Delivery \& Stakeholder Management:} Cross-functional alignment, vendor negotiation, IP strategy
\end{itemize}

%=====================
% SELECT ACHIEVEMENTS
%=====================
\section*{SELECT ACHIEVEMENTS}
\begin{itemize}[leftmargin=*]
  \item \textbf{AI-Driven Advertisement Optimization:} Led GenAI-based solutions to predict KPIs for ad creatives, transforming ways of working for marketing stakeholders.
  \item \textbf{Active Learning Platform:} Pioneered a human-in-the-loop ML pipeline at Alegion, integrating continuous feedback from annotators and automated models to boost annotation efficiency.
  \item \textbf{Candidate Screening System with LLMs:} Developed and deployed an LLM-based screening process, increasing candidate NPS by 12\%.
  \item \textbf{Multinational Data Team Expansion:} Built and scaled Overhaul's data organization; led a six-month assignment establishing a European hub in Ireland.
  \item \textbf{Large-Scale ML Pipelines:} Leveraged Prefect and DBT with Snowflake for near-real-time analytics, enabling rapid ML experimentation across international markets.
\end{itemize}

%=====================
% PROFESSIONAL EXPERIENCE
%=====================
\section*{PROFESSIONAL EXPERIENCE}

\subsection*{Director, Software and AI \hfill PMG (Feb 2024 -- Present, Austin, TX)}
\begin{itemize}[leftmargin=*]
  \item Lead AI and software engineering teams implementing advanced ML solutions for ad content optimization and KPI performance.
  \item Drive transition from descriptive to predictive analytics, integrating GenAI into creative processes to enhance ROI.
\end{itemize}

\subsection*{AI Consultant \hfill Thought and Memory LLC}
\textit{(Jan 2024 -- Mar 2024)}
\begin{itemize}[leftmargin=*]
  \item Contracted with PMG to build an ML engineering team and deliver first-generation creative-prediction models.
\end{itemize}

\textit{(Jan 2023 -- Sep 2023)}
\begin{itemize}[leftmargin=*]
  \item Developed a Large Language Model (LLM)-based candidate screening system, boosting candidate NPS by 12\%.
\end{itemize}

\textit{(Sep 2022 -- Dec 2022)}
\begin{itemize}[leftmargin=*]
  \item Built an algorithmic scheduling system for jobsite maintenance, reducing scheduling time by 50\% and overall service time by 20\%.
\end{itemize}

\subsection*{Vice President, Data Science and Analytics \hfill Overhaul, Inc. (Jun 2020 -- Aug 2022)}
\begin{itemize}[leftmargin=*]
  \item Hired as first data-focused leader; built an 8-person global team (Data Engineering, BI, and ML).
  \item Led ML efforts (transportation duration models, security event scoring), adopting Prefect/DBT to populate a Snowflake data warehouse.
  \item Oversaw a six-month Ireland-based assignment to form a regional data team and secure university partnerships.
\end{itemize}

\subsection*{Senior Director, Machine Learning \hfill Alegion, Inc. (Mar 2019 -- Apr 2020)}
\begin{itemize}[leftmargin=*]
  \item Introduced active learning workflows with AWS Sagemaker, Kubeflow, and DVC, enhancing image/video annotation by over 30\%.
  \item Identified new product SKUs, steered IP initiatives, and managed ML engineering \& architecture teams.
  \item Deployed deep learning solutions (CV \& NLP) for multiple enterprise use cases.
\end{itemize}

\subsection*{Senior Director, Data Science \hfill DOSH, LLC (Jan 2018 -- Feb 2019)}
\begin{itemize}[leftmargin=*]
  \item Launched a 9-person data organization to power Dosh’s rewards-based mobile app.
  \item Built AWS Redshift data warehouse, introduced XGBoost models for offer redemption, and consulted on fraud detection.
\end{itemize}

\subsection*{Senior Director \& Director, Data Science \& Software Engineering \hfill HomeAway (Expedia Group) (Jun 2010 -- Dec 2017)}
\begin{itemize}[leftmargin=*]
  \item \textbf{Data Science:} Formed a 25-person ML team for search ranking, content recommendations, chatbot NLP, and photo analysis.
  \item \textbf{Software Engineering:} Led a 25-person team building PCI-compliant payment systems and oversaw global revenue flows.
  \item Established an ML pipeline, introduced word2vec/image2vec-based similarity services, and shaped the organization’s data science culture.
\end{itemize}

\subsection*{Principal Software Engineer \& Manager \hfill PayPal, Inc. (Mar 2007 -- Jun 2010)}
\begin{itemize}[leftmargin=*]
  \item Developed two-factor authentication for PayPal/eBay, introduced Agile best practices, and served as Scrum Master.
\end{itemize}

\subsection*{Software Engineer \hfill Visa, Inc. (Nov 2000 -- Mar 2007)}
\begin{itemize}[leftmargin=*]
  \item Developed Verified by Visa (3D Secure) directory servers, led certification \& testing efforts.
\end{itemize}

%=====================
% EDUCATION
%=====================
\section*{EDUCATION}
\begin{itemize}[leftmargin=*]
  \item \textbf{Complex Systems Summer School}, The Santa Fe Institute (2015)
  \item \textbf{B.S. in Electrical Engineering}, University of Southern California (1990)
  \item \textbf{B.A. in Mathematics}, Carroll College (1990)
\end{itemize}

%=====================
% CERTIFICATIONS
%=====================
\section*{CERTIFICATIONS}
\begin{itemize}[leftmargin=*]
  \item Neural Networks and Deep Learning (Python/Keras), Coursera (Nov 2017)
  \item R Programming, Coursera (Sept 2014)
  \item The Data Scientist’s Toolbox, Coursera (Sept 2014)
  \item Certified ScrumMaster, Rally, Inc. (June 2008)
\end{itemize}

%=====================
% PATENTS
%=====================
\section*{PATENTS}
\begin{itemize}[leftmargin=*]
  \item \textbf{US9928498B2 (2018-03-27)} -- System, apparatus and method for segregating data in transactions via dedicated interface elements for isolated logic and repositories
  \item \textbf{US10339487B2 (2019-07-02)} -- Systems and methods to reconcile free-text with structured data
\end{itemize}

%=====================
% VOLUNTEERING & AFFILIATIONS
%=====================
\section*{VOLUNTEERING \& AFFILIATIONS}
\begin{itemize}[leftmargin=*]
  \item \textbf{Industry Adviser}, UT McCombs School of Business (2015 -- Present)
    \begin{itemize}
      \item Provided MSBA curriculum guidance; supervised three capstone projects.
    \end{itemize}
  \item \textbf{Advisory Council}, McCombs School of Business, University of Texas (Jan 2014 -- Present)
  \item \textbf{Chairman of the Board / Board Member}, Skillpoint Alliance (Feb 2012 -- Sep 2016)
  \item \textbf{Industry Consultant}, City of Austin Business \& International Affairs Focus Group (Jan 2018 -- Present)
\end{itemize}

\end{document}
